---
title: "Alcohol vs Seat choice"
author: "Matthew Ramirez"
date: "6/4/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

# Introduction
Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

The data came from UCDavis in the year...

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows.

# Methods
In the data set davisdata Seat is a categorial variable, alcohol is numerical

We try to predict alcohol ~ Seat so we use the numerical~Cat.rmd helper file

# Results

## Descriptive results

### Graphical summary

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```

```{r}
basicCN + geom_boxplot()
```

This boxplot shows that the people who wit in the back drink more alcohol than the rest.

### Numerical summary

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The numerical summary shows that mean of the back seats having a higher alcohol consumption than the other mean representing the middle and front.

### Inferential results

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The p-value is 0.000116, less than 0.05 so we reject the null hypothesis  
There is a difference in alcohol consumption based on where people sit


```{r}
plot(TukeyHSD(model1))
```

## Conclusions

The results of the p-value that was rejected by the null hypothesis doesn't make a difference due to the back seats having the most people and alcohol consumption.
